---
title: "Project Group 8"
author: Utkuhan Genc, Cole Parsons, Amanda Crowe, Collin Jewett, Kayla Parker, Michael
  Campbell, Shriya Das
date: "November 5, 2018"
output: html_document
---

```{r setup, eval  = FALSE}
install.packages("zipcode")
install.packages("generator")
install.packages("RMySQL")
install.packages("random")
install.packages("tidyr")
install.packages("sampling")
install.packages("ggmap")
install.packages("rvest")
install.packages("RMySQL")
install.packages("httr")
install.packages("XML")
install.packages("stringi")
install.packages("tidyverse")
```

```{r}
library(tidyverse) 
library(generator)
library(zipcode)
library(tidyr)
library(dplyr)
library(sampling)
library(ggmap)
library(rvest)
library(stringr)  
library(ggplot2)
library(stringi)
library(RMySQL)
```

```{r}

con <- dbConnect(MySQL(),
         user="g1090429", password="WhereHouse?",
         dbname="g1090429", host="mydb.ics.purdue.edu")
on.exit(dbDisconnect(con))



```

```{r}
all_cons <- dbListConnections(MySQL())
for (con in all_cons)
dbDisconnect(con)
```

For every owner there will be around 235 lessees, this number is found from the airbnb number of hosts(640,000) and number of users(150 million).
We have scraped 500 warehouse data from loopnet however we have omitted the warehouses that does not disclose the rent price and also omitted the ones with 

```{r user}
#USER DATATABLE
sample_size <- lesse_num + nrow(owner)


#First and Last Names
full_name <- r_full_names(sample_size)
df <- as.data.frame(full_name)
names <- tidyr::separate(df, full_name, sep = " ", c("First_name", "Last_name" ))

#User type
user_type <- as.data.frame(rbinom(sample_size, 1, nrow(owner)/ sample_size))
sum(user_type) - length(user_type)

#Phone Number
Phone_num <- r_phone_numbers(sample_size)
Phone_num <- as.data.frame(Phone_num)

#Email
Email <- r_email_addresses(sample_size)
Email <- as.data.frame(Email)

#Date of Birth 
DOB <- sample(seq(as.Date('1950/01/01'), as.Date('2000/01/01'), by="day"), sample_size, replace = TRUE )
DOB <- as.data.frame(DOB)


#Address
data <- read.csv("data.csv")
address_2 <- 0

#Password
password<- stri_rand_strings(n=sample_size, length=15, pattern="[A-Za-z0-9]")
password <- as.data.frame(password)

a <- data.frame(DOB,Phone_num, user_type, Email, password)



user <- names
user$First_name <- as.character(names$First_name)
user$Last_name <- as.character(names$Last_name)
user$Address_1 <- as.character(data$Street.Address)
user$Address_2 <- as.character(0)
user$City <- as.character(data$City)
user$State <- as.character(data$State)
user$Zipcode <- as.integer(data$Zip.Code)
user$DOB <- a$DOB
user$Phone_num <- as.integer(a$Phone_num)
user$Email <- as.character(a$Email)
user$Password <- as.character(a$password)
user <- user[, -c(1:2)]
user <- tibble::rowid_to_column(user, "id")



dbWriteTable(con, "User", user, overwrite = TRUE)




```

```{r owner}

#Company Name 
company_names <- lapply(paste0('http://www.hoovers.com/company-information/company-search.html?term=warehousing-and-storage--&nvcnt=76&maxitems=100&page=', 1:10,sep="/"),
                function(url){
                  url %>% read_html() %>% 
                    html_nodes(".company_name") %>% 
                    html_text() %>%
                    str_trim() 
                })
company_names <- unlist(company_names)
company_names<- as.data.frame(company_names)
owner <- company_names
colnames(owner)[1] <- "Company_name"

#Bank Account Number 
bank_account <- sample(10000000000:999999999999, nrow(company_names),replace=TRUE)
bank_account <- as.data.frame(bank_account)

#Routing Number
routing_number <- sample(1e9:1e10,nrow(company_names),replace=TRUE)
routing_number <- as.data.frame(routing_number)


a <- bind_cols(bank_account,routing_number)
owner$bank_acc <- a$bank_account
owner$routing_num <- a$routing_number

specific <- sample(1:1000,376)
owner <- owner[specific,]

owner <- tibble::rowid_to_column(owner, "owner_id")

dbWriteTable(con, "Owner", owner, overwrite = TRUE)

```

```{r lessee}
lesse_num <- nrow(owner) * 100
credit_card_num <- r_credit_card_numbers(lesse_num)
credit_card_num <- gsub("-","", credit_card_num)
credit_card_num <- as.data.frame(credit_card_num)
dbWriteTable(con, "Lessee", credit_card_num, overwrite = TRUE)

```

```{r warehouse}
Street <- lapply(paste0("https://www.loopnet.com/warehouses-for-lease/", 1:20,sep="/"),
                function(url){
                  url %>% read_html() %>% 
                    html_nodes(".listingTitle") %>% 
                    html_text() %>%
                    str_trim() %>%
                    gsub('-* Warehouse for Lease', '', .)
                  
              })

Street <- unlist(Street)
Street <- as.data.frame(Street)


#City and State 
city_state <- lapply(paste0('https://www.loopnet.com/warehouses-for-lease/', 1:20,sep="/"),
                 function(url){
                   url %>% read_html() %>% 
                     html_nodes(".listingDescription b") %>% 
                     html_text() %>%
                     str_trim()
                   
                 })

city_state <- unlist(city_state)
city_state <- as.data.frame(city_state)
city_state <- city_state %>% separate(city_state, sep = "," ,c("city","State"))

#Zipcodes
zipcodes <- read.csv("test.csv") %>% select("Zipcode", "ID")

#Attributes 
df1 <- lapply(paste0('https://www.loopnet.com/warehouses-for-lease/', 1:20,sep="/"),
                     function(url){
                       url %>% read_html() %>% 
                         html_nodes(".listingAttributes tr") %>% 
                         html_text() %>%
                         str_trim()
                     })

df1 <- unlist(df1)
df1 <- as.data.frame(df1)

#Price per skid per month 
price <- df1 %>% filter(str_detect(df1,"Price:")) %>%
  separate(df1, sep = ":", c("Text","Fee")) %>%
  separate(Fee, sep = "-", c("Fee", "Max"))

price$Text <- NULL
price$Max <- NULL

price$Fee <- gsub("[^0-9\\.]", "", price$Fee)
price <- as.numeric(price$Fee) 
price <- as.data.frame(price)

#Building Size 
building_size <- df1 %>% filter(str_detect(df1, "Building Size")) %>%
  separate(df1, sep = ":", c("Text", "Size"))
building_size$Text <- NULL
building_size$Size <- gsub("[^0-9\\]", "", building_size$Size) 
Size <- as.numeric(building_size$Size)
Size <- as.data.frame(Size)

#Temperature control 
temp <- c("dry", "temp_controlled", "cooler", "frozen")


#Warehouse data frame 
warehouse <- bind_cols(Street,city_state,price, Size) 
warehouse <- as.data.frame(warehouse) %>%
  mutate(price = price * 12) %>% 
  mutate(price, replace(price, price > 20, NA)) %>%
  na.omit
warehouse$`replace(price, price > 20, NA)` <- NULL
warehouse <- tibble::rowid_to_column(warehouse, "ID")
warehouse <- left_join(warehouse, zipcodes, by = "ID")
warehouse <- warehouse %>% na.omit
warehouse$temp <- sample(temp, nrow(warehouse), replace = TRUE, prob = c(.30,.50,.15,.05))
warehouse$capacity <- floor(capacity_find(warehouse$Size))
warehouse$lowest_temp[warehouse$temp == "frozen"] <- 0
warehouse$lowest_temp[warehouse$temp == "cooler"] <- 34
warehouse$lowest_temp[warehouse$temp == "temp_controlled"] <- 55
warehouse$lowest_temp[warehouse$temp == "dry"] <- 75
warehouse$highest_temp <- 75 
warehouse$rating <- round(runif(nrow(warehouse), 0, 10),1)

warehouse$freq <- 366
warehouse<- warehouse[rep(row.names(warehouse), warehouse$freq),1:9]
warehouse$used <- 0
warehouse <- bind_cols(warehouse,day)
warehouse$freq <- NULL

warehouse$id <- warehouse$ID
warehouse$adress_1 <- warehouse$Street
warehouse$adress_2 <- 0
warehouse$city <- warehouse$city
warehouse$state <- warehouse$State
warehouse$price_per_skid <- warehouse$price * 16 / 365
warehouse$capacity <- warehouse$capacity
warehouse$sq_ft <- warehouse$Size
warehouse$strg_type <- warehouse$temp
warehouse$lowest_temp <- warehouse$lowest_temp
warehouse$highest_temp <- warehouse$highest_temp
warehouse$Day <- warehouse$day
warehouse$Used <- warehouse$used
warehouse$Avg_rating <- rating
warehouse <- warehouse[, -c(1:11)]

#We generated day 
day <- seq(as.Date('2018/01/01'), as.Date('2019/01/01'), by="day")
day <- as.data.frame(day)
day <- day[rep(seq_len(nrow(day)), 375), ]





```

```{r function}
#This function is for the capacity of each warehouse depending on their size. We have used a source from 

capacity_find <- function(size){
  utilization <- rnorm(1, mean = .55)
  stack_height <- sample(c(1,2,3,4))
  capacity <- size * utilization * stack_height / 16
  return(capacity)
}
